Location of Shrimp Farms

### 2021-02-17 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed philippines shrimp points... should probably standardize the distance from coast, but for now this will do... especially since we are going to change it

# philly_world_crop <- philly_world_crop %>%
#   mutate(new_id = 1) %>%
#   group_by(new_id) %>%
#   summarise(geometry = st_union(geometry)) %>%
#   ungroup()
# 
# mapview(philly_world_crop)
# 
# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
# mapview(p_meters)
# 
# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
# mapview(buff)
# 
# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
# mapview(linestring)
# 
# ## now reproject back to original 
# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
# mapview(buffer_outline_fixed)
# 
# 
# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
# mapview(philly2)
#   
# linestring_fix <- st_difference(buffer_outline_fixed, philly) ## now grab only the outline 
# mapview(linestring_fix)

philly_crop <- as(philly_world_crop, "Spatial")
mapview(philly_crop)

philly_points_lines <- sample.line(philly_crop, n = 2) ## equally place the number of farms along the coastline 
class(philly_points_lines)
plot(philly_points_lines)

philly_points <- st_as_sf(philly_points_lines)
mapview(philly_points)

## Now filter out the points that fall outside of 271
philly_points_final <- philly_points[1:271,]
mapview(philly_points_final)

phl_pts <- st_centroid(philly_points_final)

>>>>

# philly_world_crop <- philly_world_crop %>%
#   mutate(new_id = 1) %>%
#   group_by(new_id) %>%
#   summarise(geometry = st_union(geometry)) %>%
#   ungroup()
# 
# mapview(philly_world_crop)
# 
# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters
# mapview(p_meters)
# 
# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
# mapview(buff)
# 
# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline
# mapview(linestring)
# 
# ## now reproject back to original
# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
# mapview(buffer_outline_fixed)
# 
# 
# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
# mapview(philly2)
# 
# p_meters2 <- st_transform(philly2, crs = 7801) ## transform to a crs that can buffer in meters
# mapview(p_meters2)
# 
# buff2 <- st_buffer(p_meters2, dist = 9000)
# mapview(buff2)
# intersection_fixed <- st_transform(buff2, crs = crs(philly_world_crop))
# mapview(intersection_fixed)
# 
# linestring_fix <- st_difference(buffer_outline_fixed, intersection_fixed) ## now grab only the outline
# mapview(linestring_fix)

p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters
mapview(p_meters)

buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

philly_crop <- as(buff, "Spatial")
mapview(philly_crop)

fix <- as(philly_crop, "SpatialLinesDataFrame")
class(fix)
mapview(fix)

philly_points_lines <- sample.line(fix, n = 80) ## equally place the number of farms along the coastline 
class(philly_points_lines)
plot(philly_points_lines)

philly_points <- st_as_sf(philly_points_lines) %>%
  mutate(new_id = 1:560)
mapview(philly_points)

philly_points_fix <- philly_points %>%
  filter(new_id %in% c(241:285, 1:47, 161:201, 321:361, 481:523, 401:446, 81:123)) %>%
  filter(!(new_id %in% c(23:27, 32, 184, 298, 300, 303, 273, 280, 63, 57, 242:244, 88, 79, 123, 112, 125, 127, 153, 424:427, 90, 496:497, 198, 193, 191, 182, 170, 515:516, 328, 276, 9, 168:170, 82)))

mapview(philly_points_fix)

# ## Now filter out the points that fall outside of 271
# philly_points_final <- philly_points[1:271,]
# mapview(philly_points_final)

phl_pts <- st_centroid(philly_points_fix)
